---
title: Alvaro Gerns's Resume"
author: Alvaro Gerns
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)
# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE
# Holds all the links that were inserted for placement at the end
links <- c()
source('parsing_functions.R')
# Load csv with position info
position_data <- read_csv('positions.csv') 



```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```

Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------


- <i class="fa fa-envelope"></i> alvarogerns@yahoo.de
- <i class="fa fa-skype"></i> <a href="skype:live:alvarogerns?call">live:alvarogerns</a>
- <i class="fa fa-linkedin"></i>  [Alvaro Gerns](https://linkedin.com/in/alvarogerns)
- <i class="fa fa-phone"></i> +41 775065971



Language Skills {#skills}
--------------------------------------------------------------------------------

```{r}
skills <- tribble(
  ~skill,               ~level,
  "German",             5,
  "Spanish",            5,
  "English",            5,
  "French",             3
)
build_skill_bars(skills)
```




IT skills {#skills2}
--------------------------------------------------------------------------------

```{r}
skills2 <- tribble(
  ~skill,               ~level,
  "R",                  5,
  "Stata",              5,
  "Tableau",            4.5,
  "LaTeX",              4,
  "Python",             2
)
build_skill_bars(skills2)
#Credits on template to [Nick Strayer](https:github.com/nstrayer/cv)

#Publications {#more-info}
#--------------------------------------------------------------------------------


```



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------


Last updated on `r Sys.Date()`.


Main
================================================================================

Alvaro Gerns Jimenez-Villarejo {#title}
--------------------------------------------------------------------------------

```{r}
intro_text <- "A research-oriented individual that is looking to engage further in the field of development aid through the lens of evidence-based policy making; particularly interested in the knowledge transfer and translation between research and policy and how we can process already available evidence on poverty eradication. He is a passionate climber and hobby painter."
cat(sanitize_links(intro_text))
```




Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```



Work Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'work_experience')
```



Industry Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

::: aside
I have worked in a variety of roles ranging from journalist to software engineer to data scientist. I like collaborative environments where I can learn from my peers. 
:::

```{r, eval=FALSE, eval=FALSE}
print_section(position_data, 'industry_positions')
```

<br>
<br>
<br>

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

::: aside
I am passionate about education. I believe that no topic is too complex if the teacher is empathetic and willing to think about new methods of approaching task. 
:::

```{r, eval=FALSE}
print_section(position_data, 'teaching_positions')
```


Selected Data Science Writing {data-icon=chart-line}
--------------------------------------------------------------------------------


::: aside
Other shit
:::

```{r, eval=FALSE}
print_section(position_data, 'data_science_writings')
```



Selected Press (About)  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r, eval=FALSE}
print_section(position_data, 'about_me_press')
```



Selected Press (By)  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r, eval=FALSE}
print_section(position_data, 'by_me_press')
```




Selected Publications, Posters, and Talks {data-icon=book}
--------------------------------------------------------------------------------

```{r, eval=FALSE}
print_section(position_data, 'academic_articles')
```



```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------
<br>
")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```




